---
title: "Investigating how administrative burden and information costs affect social inequalities
  in early childcare access, a randomised controlled trial"
author: "Manuscript submitted to Nature Human Behaviour"
bibliography: NHB.bib
csl: nature.csl
abstract: |
  Low socioeconomic status (SES) and immigrant households benefit the most from attending high-quality early childcare, but they often access it the least. This study tests whether cognitive and behavioural barriers contribute to these access gaps in the French context, where disparities in early childcare enrolment are large. Through a multi-arm experiment, we evaluate the effectiveness of informational interventions and personalised support to enhance early childcare application and access in a sample of 1,849 households. Results revealed that the information-only treatment had minimal impact, while adding personalised support to alleviate administrative burdens significantly bridged the SES and migration gaps in early childcare applications. However, despite substantial increases in application rates, we found limited impacts on access rates for low-SES and immigrant households. Our research underscores the need for integrated strategies to promote equal opportunities in early childhood education by identifying key obstacles to early childcare access for these households.

always_allow_html: true
language:
  label:
    fig: 'Figure '
    tab: 'Table '
    eq: 'Equation '
output: 
    bookdown::word_document2: 
      reference_docx: FormatRefWordFinal.docx
      fig_caption: yes
      toc: no
    officedown::rdocx_document:
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message=FALSE, warning=FALSE,fig.width = 8,fig.height = 5,fig.pos = "H" #, 
#cache.lazy = FALSE)
)
doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
library(pacman)
p_load(here)
p_load(officedown)
```

```{r LoadLibraries, include=FALSE}
source(here("RScripts","LoadInstallPackages.R"), local = knitr::knit_global())
```

```{r LoadData, include=FALSE}
source(here("RScripts","LoadAllData.R"), local = knitr::knit_global())
```

```{r ImportAllFunctions, include=FALSE}
source(here("RScripts","AllFunctions.R"), local = knitr::knit_global())
```

```{r, include=FALSE, cache=FALSE}
knitr::read_chunk(here("RScripts","MainAnalyses.R"))
# This file contains all the chunks of codes to be called at the right place in the Rmarkdown document
```

\newpage

# Introduction

```{r Intro, child='Sections/S1_Introduction.Rmd'}
```

# Results

```{r Results, child='Sections/S2_Results.Rmd'}
```

# Discussion

```{r Discussion, child='Sections/S3_Discussion.Rmd'}
```

# Methods

```{r Methods, child='Sections/S4_Methods.Rmd'}
```

# Bibliography {.unnumbered}

::: {#refs}
:::

**Data availability** Data availability This study used primary outcome data collected through surveys. The anonymised data is available for replication on OSF at the following link: <https://osf.io/rh7eb/?view_only=ef7409ac646544eaac946374de134892>.

**Code availability** The code to replicate this article, including analysis and tables, is publicly available on OSF at the following link: <https://osf.io/rh7eb/?view_only=ef7409ac646544eaac946374de134892>. All analyses were performed using R 4.3.0 and R studio 2023.12.1. \newpage

# Extended Data {.unnumbered}

```{r ExtendedData, child='Sections/S5_ExtendedData.Rmd'}
```
